---
title: "So, what about feet?"
output: github_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE, echo = FALSE}
library("worcs")
# This is a convenience function for reporting statistics in manuscripts
report <- function (x, digits = 2, equals = TRUE){
  equal_sign <- "= "
  if (abs(x) < 10^-digits) {
    equal_sign <- "< "
    outstring <- 10^-digits
  } else {
    outstring <- formatC(x, digits = digits,format = "f")
  }
  paste0(equal_sign, outstring)
}
# Set some options for the way code is displayed
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

I was curious to find out whether there is a difference in mean shoe size between men and women, so I did a little study with a convenience sample of attendees at the Open Science Festival.

This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency. All code <!--and data--> are available at <https://github.com/cjvanlissa/pac_demo.git>.

<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
`r notify_synthetic()`

# Analysis

I performed a t-test, which is sourced here from the file `analysis.R`:

```{r analysis, file = "../analysis.R"}
```

# Results

There was a `r c("non-significant", "significant")[(result[["p.value"]] < .05)+1]` difference between men's ($M `r report(result[["estimate"]][1])`$)
and women's men's ($M `r report(result[["estimate"]][2])`$)
shoe sizes, $p `r report(result[["p.value"]])`$.

Shoe sizes were distributed as follows:

```{r histogram, echo=FALSE}
library(ggplot2)
ggplot(data = dat, aes(x = shoesize, color = sex, fill = sex)) +
  geom_density(alpha = .2) +
  theme_bw()
```

# References
